#Questions


- is fsend_i always decreasing?   **Answer:** No. Check Morehouse. A blip at 5. \\\\/ shape. (I assume 5 is the max and the ambitious tryers will max out.)
- do rows (colleges) with PrivacySuppressed or NULL actually display some data?  
- compare histograms of income to US averages 
- subtract family income from student income 
- NWNE? WNE?
- the counts nearly always integer?
- pct_ba = ?  It's not black + asian (tested ✓)
- lowest % aged under 24, lowest age of entry, % independent
- inequality amongst schools (mean/median ratio of hh inc)
- how well do various measures of "independent" go together? (married, veteran, agesquared…)
- how well do pell grants go with low hh income?
- can you use these stats to gauge 


#### ending p means…?

they are cohorts.
- p6 is 6 years after graduation.
- p10 is 10 years after graduation.

### fsend means … ?

how many FAFSA forms 

Two uses:
- how many people filled out fafsa's (measure of aid, vs say poverty or log hh inc)
- how many people conscientiously / competitively applied to many schools










# TODO


- look at quantiles 
- look at mean, median, sd, squares, etc 
- mean vs median
- √squared age − age ✓
- log versus log of total


```{r difference.in.logs}
#na.omit(earnings$ln_median_hh_inc) - na.omit(log(earnings$median_hh_inc)) %>% some(500) %>% stem
#na.omit(earnings$ln_median_hh_inc) - na.omit(log(earnings$median_hh_inc)) %>% kd
{ earnings$ln_median_hh_inc - log(earnings$median_hh_inc) } %>% stem
{ earnings$ln_median_hh_inc - log(earnings$median_hh_inc) } %>% na.omit %>% kd
```

OK, so this is just a computed column.


- sort by highest standard deviation (greatest wage dispersion)
- look at quantiles
- other measures of wage dispersion of graduates
- try to account for starting income (how??)
- try to adjust ratio of mean:median for low incomes generally being easier to get in 2:1 ratio
- try to adjust high SD's for same


Maybe just SD / mean is good enough?



- look at mens' versus womens' colleges. (hah!)
- (but take out beauty schools)








#Interesting Subsets

## lot of graduates make <25k
- cosmetology schools, naturopathy

## almost all graduates make >25k
- schools in New York (can I take out family income?)
- RPI, Bentley, Lehigh
- (call this "risk factor")



# Interesting fields

- loan ever
- pell ever
- age & age²
- minority, female, race, dependents, veteran



Goal to subset or "mod out" by these?





# sort by

- % white
- really low incomes
- log median hh income
- sent FAFSA to a lot of other schools
- serving veterans, poor, low hh income














## Schools with the greatest "age curvature" (√age²−age)
Canada College
Laurel University
King's University
Mesalands Community College
Coastline Community College
Industrial Technical College
Southeastern Baptist College
Institucion Chaviano de Mayaguez
Prince Institute-Southeast
Austin Graduate School of Theology
College of Business and Technology-Kendall
Dawson Community College
Cornerstone University
Trinity College of Florida
San Jose City College
Institute of American Indian and Alaska Native Culture
StenoTech Career Institute-Fairfield
Charles Stuart School of Diamond Setting
Faith Evangelical College & Seminary
Mountwest Community and Technical College
Computer Tutor Business and Technical Institute
Lexington College
Crossroads Bible College
Precision Manufacturing Institute
Epic Bible College
Ventura Adult and Continuing Education
Heritage Bible College
Los Angeles City College
Nyack College
East West College of Natural Medicine
Washington County Career Center-Adult Technical Training
Springfield College
Advanced College
Northwest Technology Center-Alva
Northwest Technology Center-Fairview
Geneva College
Globe Institute of Technology
Phagans Newport Academy of Cosmetology Careers
Eastern Oklahoma County Technology Center
Community Christian College
Pennsylvania Academy of the Fine Arts
Lebanon College
Moler Barber College
Bramson ORT College
Manhattan School of Computer Technology




## Schools with the highest ratio of mean : median family income
```
Austin Graduate School of Theology
Albany Medical College
House of Heavilin Beauty College-Raymore
The Creative Circus
University of Texas Southwestern Medical Center
Commonwealth Technical Institute
Lincoln University
Paul Mitchell the School-Louisville
South Baylo University
Apex Academy of Hair Design Inc
International Barber & Style College
HRDE-Stanley Technical Institute-Clarksburg
HRDE-Stanley Technical Institute-Parkersburg
Spanish-American Institute
Huertas College
Sierra College of Beauty
Leech Lake Tribal College
MTI Business College Inc
Medical College of Wisconsin
Camelot College
Sherman College of Straight Chiropractic
Hair Academy of Safford
Meharry Medical College
Sh'or Yoshuv Rabbinical College
Jenny Lea Academy of Cosmetology
Mount Angel Seminary
Midwestern University-Downers Grove
Midwestern University-Glendale
ICDC College
Hunter Business School
Travel Institute of the Pacific
Nouvelle Institute
Cain's Barber College Inc
International Training Careers
Stone Child College
College of Micronesia-FSM
EDP University of Puerto Rico Inc-San Sebastian
EDP Univeristy of Puerto Rico Inc-San Juan
Garrett-Evangelical Theological Seminary
Talmudic College of Florida
Northeast Ohio Medical University
Trend Barber College
New York College of Podiatric Medicine
The English Center
Dayton Barber College
Florida Education Institute
Studio Jewelers
Caribbean Forensic and Technical College
Five Branches University
House of Heavilin Beauty College-Kansas City
La Belle Beauty Academy
Claremont School of Theology
Massachusetts School of Barbering
Charles A Jones Career and Education Center
Advance Science Institute
```

### ok, but how about non-low family income *and* high ratio of mean:median ?

















# Schools with greatest standard deviation of 10-year incomes
```
A T Still University of Health SciencesMedical College of Wisconsin
West Virginia School of Osteopathic Medicine
Stanford University
Rosalind Franklin University of Medicine and Science
Massachusetts Institute of Technology
King's University
Harvard University
Princeton University
University of Pennsylvania
Baylor College of Medicine
Upstate Medical University
University of North Texas Health Science Center
Meharry Medical College
Amherst College
The University of Texas Health Science Center at Houston
University of Chicago
SUNY Downstate Medical Center
University of Massachusetts Medical School Worcester
Carnegie Mellon University
Duke University
University of Texas Southwestern Medical Center
Yale University
Albany Medical College
Monterey Institute of International Studies
Middlebury College
Philadelphia College of Osteopathic Medicine
The Juilliard School
Dartmouth College
University of California-Hastings College of Law
Columbia University in the City of New York
New York Medical College
Babson College
Georgetown University
The University of Texas Health Science Center at San Antonio
University of California-San Francisco
Weill Cornell Medical College
Cornell University
Swarthmore College
Tufts University
Western University of Health Sciences
California Institute of the Arts
Golden Gate University-Silicon Valley
Golden Gate University-Seattle
Golden Gate University-Los Angeles
Golden Gate University-San Francisco
Midwestern University-Glendale
Midwestern University-Downers Grove
Brown University
New York University
Williams College
Northwestern University
University of Notre Dame
University of Nebraska Medical Center
University of Colorado Denver
Rush University
Medical University of South Carolina
Lafayette College
Colgate University
Brooklyn Law School
```




# Harvard vs MIT

```{r}
earnings %>% select(INSTNM, loan_ever, age_entry, age_curvature, veteran, faminc, income_inequality, fsend_count, fsend_1, fsend_5, mn_earn_wne_p7, sd_earn_wne_p7, sd_earn_wne_p6, gt_25k_p7) %>% arrange(sd_earn_wne_p6) %>% na.omit %>% tail(25) %>% select(INSTNM, faminc, income_inequality, gt_25k_p7, mn_earn_wne_p7, sd_earn_wne_p7)
```



                                               INSTNM faminc income_inequality
5910                           Wake Forest University 124215               1.2
5911  University of North Texas Health Science Center  22394               1.5
5912              Midwestern University-Downers Grove  24971               3.0
5913                   Midwestern University-Glendale  24971               3.0
5914        University of New Hampshire-School of Law  14332               1.6
5915                       Baylor College of Medicine  14305               2.2
5916          A T Still University of Health Sciences  19377               1.4
5918                                Dartmouth College 102622               1.3
5919                                  Yale University  73769               1.6
5920                            Georgetown University  87179               1.4
5921 University of California-Hastings College of Law  21104               1.6
5922      Columbia University in the City of New York  59265               1.9
5923          Thunderbird School of Global Management  36890               1.2
5924                              Brooklyn Law School  17727               1.9
5925                            University of Chicago  75760               1.4
5926                           Albany Medical College  10946               2.5
5927                          Meharry Medical College  18327               2.9
5928                                  Duke University  92670               1.3
5929                     Medical College of Wisconsin  13577               2.7
5930                       University of Pennsylvania  87201               1.4
5931                             Princeton University  89090               1.8
5932                               Harvard University  60646               1.8
5933                              Boise Bible College  44069               1.2
5934                              Stanford University  83178               1.5
5935            Massachusetts Institute of Technology  95849               1.2





That's right: family incomes at MIT are *higher* than those at Harvard, by about 50%. There is also a great deal of variation in family incomes at Harvard / Stanford / Yale / Dartmouth.

The `income_inequality` measure is one I dreamt up (should put that command in the dplyr command instead of the dataset ... will do on cleanup). It's the ratio of family income to median family income. [^It turned out to be a problematic measure because a lot of the cosmetology schools will have low enough of both sorts — going along with being independent = lower income than parents — that you can get super-high ratios, like 10k : 5k. Central measures like mean and median aren't going to end up as rich as the richest parents, so even schools .1%'ers send their kids to don't get 2:1 ratios. There are enough poor people, though, that median incomes at cosmetology schools can get quite low and throw up the ratio.]



Also … nice use of "global management", Thunderbird. Your family incomes are 36k. Quite global, ain't it?






# quantiles of the educated

```
<earnings csvcut -c 2,43,49,50,51,52 | grep -v Privacy | csvsort -c 2 | csvlook
```

(`grep -v` is inverted match. Useful one here!)


```
|------------------------------------------------------------------------------------------------+----------------+--------------------+--------------------+--------------------+---------------------|
|  INSTNM                                                                                        | sd_earn_wne_p9 | pct10_earn_wne_p10 | pct25_earn_wne_p10 | pct75_earn_wne_p10 | pct90_earn_wne_p10  |
|------------------------------------------------------------------------------------------------+----------------+--------------------+--------------------+--------------------+---------------------|
|  New Beginning College of Cosmetology                                                          |                |                    |                    |                    |                     |
|  Selma University                                                                              |                |                    |                    |                    |                     |
|  Troy University-Global Campus                                                                 |                |                    |                    |                    |                     |
|  Alaska Bible College                                                                          |                |                    |                    |                    |                     |
|  Global MBA Latin American Managers Program Satellite Campus                                   |                |                    |                    |                    |                     |
|  Frank Lloyd Wright School of Architecture                                                     |                |                    |                    |                    |                     |
|  Arkansas Beauty College                                                                       |                |                    |                    |                    |                     |
|  Career Academy of Hair Design-Fayetteville                                                    |                |                    |                    |                    |                     |
|  Shorter College                                                                               |                |                    |                    |                    |                     |
|  American Academy of Dramatic Arts-Los Angeles                                                 |                | 3700               | 12800              | 46400              | 58900               |
|  Phillips Graduate Institute                                                                   |                |                    |                    |                    |                     |
|  Sofia University                                                                              |                |                    |                    |                    |                     |
|  Northeastern University                                                                       | 41700          | 18800              | 38500              | 84500              | 112700              |
|  Rutgers University-Camden                                                                     | 41900          | 15400              | 35400              | 77800              | 108100              |
|  Rutgers University-New Brunswick                                                              | 41900          | 15400              | 35400              | 77800              | 108100              |
|  Rutgers University-Newark                                                                     | 41900          | 15400              | 35400              | 77800              | 108100              |
|  Regis University                                                                              | 42400          | 15100              | 33700              | 76100              | 99900               |
|  California Polytechnic State University-San Luis Obispo                                       | 42600          | 15700              | 37900              | 86400              | 112300              |
|  University of Connecticut                                                                     | 42700          | 19000              | 35900              | 74800              | 101800              |
|  National Louis University                                                                     | 42700          | 9600               | 25000              | 67100              | 101300              |
|  Beth Medrash Govoha                                                                           | 43000          | 3500               | 10300              | 55000              | 94200               |
|  William Penn University                                                                       | 43100          | 10700              | 26800              | 56800              | 76800               |
|  San Jose State University                                                                     | 43200          | 13200              | 31200              | 80300              | 107600              |
|  Xavier University of Louisiana                                                                | 43200          | 13300              | 28600              | 81700              | 127300              |
|  Cabrillo College                                                                              | 43300          | 6100               | 15000              | 52200              | 81800               |
|  University of San Diego                                                                       | 43400          | 14500              | 37100              | 81600              | 113700              |
|  De Anza College                                                                               | 43500          | 8400               | 22500              | 68400              | 98700               |
|  Alfred University                                                                             | 43500          | 13400              | 26500              | 62400              | 84700               |
|  Santa Barbara City College                                                                    | 43600          | 5200               | 17200              | 54200              | 80600               |
|  Loyola Marymount University                                                                   | 43800          | 17300              | 35700              | 81600              | 113000              |
|  Art Center College of Design                                                                  | 43900          | 7600               | 20900              | 85000              | 114700              |
|  Hesston College                                                                               | 43900          | 9100               | 20500              | 50300              | 67500               |
|  University of Phoenix-Phoenix Campus                                                          | 44000          | 13300              | 32300              | 79600              | 110100              |
|  Saint Johns River State College                                                               | 44000          | 7100               | 15900              | 47100              | 64300               |
|  Dominican University of California                                                            | 44100          | 9700               | 27000              | 77500              | 124200              |
|  Menlo College                                                                                 | 44200          | 11000              | 29600              | 78600              | 115800              |
|  John Brown University                                                                         | 44300          | 11800              | 29500              | 74800              | 106800              |
|  University of Arkansas                                                                        | 44400          | 13000              | 27800              | 63000              | 87200               |
|  Wayne State University                                                                        | 44400          | 10100              | 23800              | 61900              | 93500               |
|  University of Hawaii at Manoa                                                                 | 44500          | 12200              | 28000              | 61900              | 89000               |
|  Michigan State University                                                                     | 44500          | 17200              | 33100              | 72200              | 98200               |
|  DePaul University                                                                             | 44700          | 12200              | 30700              | 73600              | 99700               |
|  Illinois Institute of Technology                                                              | 44800          | 22400              | 42500              | 91400              | 118200              |
|  Loyola University Maryland                                                                    | 44800          | 24400              | 44800              | 86700              | 123600              |
|  Bates College                                                                                 | 44900          | 17500              | 34800              | 76500              | 114000              |
|  American University                                                                           | 45000          | 15000              | 35800              | 81100              | 110700              |
|  Highlands College of Montana Tech                                                             | 45000          | 10300              | 21600              | 68300              | 103700              |
|  Montana Tech of the University of Montana                                                     | 45000          | 10300              | 21600              | 68300              | 103700              |
|  The New England Conservatory of Music                                                         | 45200          | 5500               | 14200              | 48500              | 68400               |
|  Thomas Edison State College                                                                   | 45200          | 7000               | 22300              | 75900              | 115000              |
|  University of Missouri-Kansas City                                                            | 45300          | 11200              | 26300              | 66300              | 109500              |
|  Pomona College                                                                                | 45500          | 17200              | 34300              | 75500              | 133700              |
|  Notre Dame de Namur University                                                                | 45600          | 12100              | 29700              | 73900              | 96200               |
|  Thomas More College                                                                           | 45800          | 12500              | 30200              | 65800              | 97100               |
|  Auburn University                                                                             | 45900          | 13800              | 29900              | 66200              | 91400               |
|  Fairfield University                                                                          | 45900          | 28300              | 48300              | 93700              | 125500              |
|  Quinnipiac University                                                                         | 45900          | 21100              | 40100              | 77600              | 102400              |
|  University of Denver                                                                          | 46100          | 13000              | 31100              | 77400              | 105000              |
|  Palmer College of Chiropractic-Davenport                                                      | 46100          | 8600               | 18800              | 63600              | 100200              |
|  California Maritime Academy                                                                   | 46200          | 18800              | 50000              | 110300             | 141200              |
|  University of Colorado Boulder                                                                | 46200          | 12700              | 28900              | 70400              | 99400               |
|  Colorado School of Mines                                                                      | 46200          | 25400              | 52600              | 98500              | 136700              |
|  Mills College                                                                                 | 46400          | 6400               | 21000              | 59400              | 81300               |
|  Boston University                                                                             | 46400          | 19500              | 39500              | 85100              | 119600              |
|  Loyola University Chicago                                                                     | 46600          | 15900              | 33300              | 70100              | 96900               |
|  Drake University                                                                              | 46600          | 20100              | 36000              | 92800              | 130200              |
|  Samford University                                                                            | 46700          | 12600              | 27700              | 74400              | 124000              |
|  Louisiana State University Health Sciences Center-New Orleans                                 | 46800          | 25400              | 44200              | 84200              | 117200              |
|  California Western School of Law                                                              | 47100          | 23100              | 57700              | 122500             | 154300              |
|  MCPHS University                                                                              | 47100          | 36200              | 73800              | 138300             | 155500              |
|  Academy of Art University                                                                     | 47300          | 5900               | 17700              | 62100              | 90600               |
|  University of San Francisco                                                                   | 47300          | 18000              | 37600              | 92800              | 122100              |
|  Illinois College of Optometry                                                                 | 47400          | 27000              | 52700              | 112300             | 142500              |
|  University of California-San Diego                                                            | 47800          | 17800              | 38200              | 88100              | 122700              |
|  Albany College of Pharmacy and Health Sciences                                                | 47900          | 33000              | 58500              | 137800             | 151900              |
|  Foothill College                                                                              | 48000          | 7300               | 21400              | 83500              | 117600              |
|  Maine Maritime Academy                                                                        | 48000          | 22900              | 38800              | 108600             | 151100              |
|  Carleton College                                                                              | 48100          | 11800              | 30100              | 66600              | 105200              |
|  University of Louisville                                                                      | 48500          | 10200              | 23600              | 55200              | 76600               |
|  Loma Linda University                                                                         | 48900          | 22600              | 47900              | 98700              | 133800              |
|  University of California-Davis                                                                | 49100          | 16900              | 36700              | 85500              | 117500              |
|  St Louis College of Pharmacy                                                                  | 49100          | 31800              | 47600              | 132600             | 147900              |
|  Bentley University                                                                            | 49200          | 30100              | 50900              | 99400              | 130700              |
|  The University of Alabama                                                                     | 49300          | 13100              | 27900              | 60700              | 85000               |
|  Louisiana State University and Agricultural & Mechanical College                              | 49400          | 14400              | 30300              | 68100              | 96600               |
|  Mount St Mary's College                                                                       | 49500          | 14300              | 31800              | 77900              | 103700              |
|  Mount St. Mary's College - Doheny Campus                                                      | 49500          | 14300              | 31800              | 77900              | 103700              |
|  Connecticut Center for Massage Therapy-Newington                                              | 49700          | 5000               | 11500              | 48900              | 71600               |
|  Saint Mary's College of California                                                            | 49800          | 15500              | 36800              | 89400              | 127400              |
|  College of the Canyons                                                                        | 50300          | 5400               | 17000              | 54400              | 79400               |
|  Harvey Mudd College                                                                           | 50800          | 24500              | 45400              | 106800             | 146900              |
|  Saint Johns University                                                                        | 50900          | 26100              | 39400              | 77000              | 107400              |
|  William Mitchell College of Law                                                               | 51000          | 31500              | 48800              | 97800              | 148300              |
|  Georgia Institute of Technology-Main Campus                                                   | 51100          | 23700              | 49000              | 98300              | 130000              |
|  Life University                                                                               | 51100          | 7100               | 14400              | 56700              | 90300               |
|  Los Medanos College                                                                           | 51600          | 4000               | 14300              | 53600              | 79900               |
|  Charles R Drew University of Medicine and Science                                             | 52200          | 7900               | 23800              | 107800             | 136200              |
|  University of Maryland-College Park                                                           | 52200          | 19100              | 40400              | 82900              | 111500              |
|  University of Iowa                                                                            | 52300          | 17300              | 33500              | 69600              | 101700              |
|  University of Illinois at Urbana-Champaign                                                    | 53000          | 20800              | 38000              | 82300              | 112000              |
|  University of Illinois at Chicago                                                             | 53200          | 14300              | 31900              | 74300              | 106700              |
|  University of Mississippi                                                                     | 53600          | 13200              | 27500              | 62100              | 96700               |
|  University of Mississippi Medical Center                                                      | 53600          | 13200              | 27500              | 62100              | 96700               |
|  Maine College of Art                                                                          | 53700          | 4300               | 11200              | 36100              | 45100               |
|  College of the Holy Cross                                                                     | 53900          | 31000              | 47200              | 92200              | 136800              |
|  Brandeis University                                                                           | 54200          | 17900              | 39600              | 82700              | 121300              |
|  Berk Trade and Business School                                                                | 54200          | 3800               | 13700              | 63200              | 83600               |
|  Southwestern Law School                                                                       | 54400          | 13600              | 39200              | 114300             | 147700              |
|  University of the Pacific                                                                     | 54500          | 15900              | 38200              | 116100             | 154800              |
|  Worcester Polytechnic Institute                                                               | 54700          | 28200              | 53500              | 96600              | 117100              |
|  California College of the Arts                                                                | 55000          | 3300               | 14700              | 63100              | 100300              |
|  Barnard College                                                                               | 55000          | 17400              | 36600              | 82000              | 127400              |
|  University of California-Los Angeles                                                          | 55200          | 13900              | 36700              | 88600              | 128000              |
|  Portfolio Center                                                                              | 55400          | 2900               | 15500              | 77800              | 137700              |
|  Marshall B Ketchum University                                                                 | 55600          | 17700              | 40900              | 107900             | 153900              |
|  Pepperdine University                                                                         | 56000          | 15200              | 37300              | 94600              | 137800              |
|  Stevens Institute of Technology                                                               | 56200          | 32100              | 60700              | 105300             | 135300              |
|  Claremont McKenna College                                                                     | 56500          | 18200              | 44300              | 107800             | 164000              |
|  Trinity College                                                                               | 56600          | 18200              | 37600              | 82900              | 126800              |
|  Golden Gate University-San Francisco                                                          | 57100          | 18200              | 39000              | 94300              | 122800              |
|  Golden Gate University-Los Angeles                                                            | 57100          | 18200              | 39000              | 94300              | 122800              |
|  Golden Gate University-Seattle                                                                | 57100          | 18200              | 39000              | 94300              | 122800              |
|  Golden Gate University-Silicon Valley                                                         | 57100          | 18200              | 39000              | 94300              | 122800              |
|  University of Southern California                                                             | 57100          | 15800              | 39400              | 99000              | 143900              |
|  National University of Health Sciences                                                        | 57100          | 6800               | 22000              | 65100              | 95900               |
|  George Washington University                                                                  | 57400          | 19300              | 42100              | 96100              | 137200              |
|  Bowdoin College                                                                               | 57800          | 15300              | 35500              | 80300              | 135100              |
|  Santa Clara University                                                                        | 57900          | 21600              | 45000              | 99200              | 139000              |
|  Colby College                                                                                 | 60500          | 15400              | 35000              | 74300              | 111700              |
|  Samuel Merritt University                                                                     | 62000          | 30700              | 65000              | 138800             | 194400              |
|  Rush University                                                                               | 62300          | 33600              | 53100              | 131100             | 242500              |
|  University of Maryland-Baltimore                                                              | 62300          | 35900              | 58400              | 119800             | 158600              |
|  Washington University in St Louis                                                             | 62300          | 20200              | 40500              | 96600              | 154300              |
|  Wesleyan University                                                                           | 62400          | 11400              | 29800              | 71900              | 105200              |
|  Wellesley College                                                                             | 62800          | 18600              | 39100              | 80500              | 121300              |
|  University of Michigan-Ann Arbor                                                              | 62900          | 17200              | 37500              | 87500              | 128000              |
|  University of California-Berkeley                                                             | 64300          | 16200              | 38500              | 97600              | 149700              |
|  University of Colorado Denver                                                                 | 64400          | 21700              | 42200              | 125800             | 157000              |
|  Coffeyville Community College                                                                 | 64700          | 5100               | 16200              | 44700              | 64800               |
|  Coffeyville Technical Campus                                                                  | 64700          | 5100               | 16200              | 44700              | 64800               |
|  Columbus Technical Campus                                                                     | 64700          | 5100               | 16200              | 44700              | 64800               |
|  Johns Hopkins University                                                                      | 65000          | 23400              | 47900              | 102800             | 148600              |
|  Emory University                                                                              | 65800          | 18300              | 38400              | 90800              | 135900              |
|  Tulane University of Louisiana                                                                | 65900          | 13700              | 32000              | 83300              | 126000              |
|  University of Miami                                                                           | 67800          | 12300              | 31400              | 77800              | 112900              |
|  Albany Law School                                                                             | 70300          | 16700              | 46100              | 96500              | 134600              |
|  Boston College                                                                                | 70400          | 24200              | 45100              | 100200             | 160300              |
|  University of Nebraska Medical Center                                                         | 71600          | 29300              | 46100              | 102600             | 159300              |
|  California Institute of the Arts                                                              | 72400          | 5400               | 14900              | 60300              | 96900               |
|  Williams College                                                                              | 75100          | 16800              | 39100              | 97000              | 167700              |
|  University of Notre Dame                                                                      | 75200          | 26000              | 47400              | 103000             | 154400              |
|  Midwestern University-Downers Grove                                                           | 78000          | 43500              | 77700              | 151900             | 244200              |
|  Northwestern University                                                                       | 80500          | 16800              | 40900              | 99400              | 173600              |
|  Tufts University                                                                              | 86100          | 21600              | 45800              | 104000             | 170300              |
|  Babson College                                                                                | 87000          | 36700              | 57500              | 124700             | 186700              |
|  University of California-San Francisco                                                        | 87900          | 40300              | 75600              | 172100             | 250000              |
|  Georgetown University                                                                         | 92300          | 28500              | 52200              | 136500             | 221900              |
|  Western University of Health Sciences                                                         | 94100          | 33200              | 76200              | 156700             | 248500              |
|  Dartmouth College                                                                             | 94100          | 16900              | 42400              | 119600             | 210500              |
|  University of Chicago                                                                         | 98700          | 16700              | 39100              | 110500             | 195000              |
|  University of California-Hastings College of Law                                              | 100700         | 25800              | 56700              | 152000             | 240200              |
|  Yale University                                                                               | 100800         | 15400              | 42400              | 116600             | 184800              |
|  Monterey Institute of International Studies                                                   | 106400         | 13900              | 33100              | 84800              | 165400              |
|  Rosalind Franklin University of Medicine and Science                                          | 106400         | 53000              | 89800              | 250000             | 250000              |
|  California Institute of Technology                                                            | 111800         | 19900              | 41400              | 125400             | 189000              |
|  Princeton University                                                                          | 115600         | 20800              | 46700              | 134800             | 217200              |
|  Amherst College                                                                               | 123900         | 18200              | 36400              | 90300              | 172500              |
|  Harvard University                                                                            | 127000         | 24700              | 51600              | 170100             | 250000              |
|  Massachusetts Institute of Technology                                                         | 143900         | 30400              | 55600              | 140300             | 242300              |
|------------------------------------------------------------------------------------------------+----------------+--------------------+--------------------+--------------------+---------------------|
```




So there you have it: sorting by standard deviation is what really leaves the famous names at top. And it really is true that going to Harvard does not guarantee you will be rich thereafter. [^With the way the government parsed this dataset — which I should say is very, very clean and nicely fixed up for us, by data-science standards — we can't tell, within Harvard, whether it was the children of the rich families who ended up in the higher brackets and the children of the poor families in the
poor. (I hold 2 conflicting stereotypes: 1. rich kids don't need the money so they will pursue their dream, being a musician or priest or whatever; 2. rich kids have great connections so they get into Wall Street / Hamptons world better.) ] Let's look at just the 90/10 splits there:


```
|------------------------------------------------------------------------------------------------+----------------+--------------------+---------------------|
|  INSTNM                                                                                        | sd_earn_wne_p9 | pct10_earn_wne_p10 | pct90_earn_wne_p10  |
|------------------------------------------------------------------------------------------------+----------------+--------------------+---------------------|
|  New Beginning College of Cosmetology                                                          |                |                    |                     |
|  Selma University                                                                              |                |                    |                     |
|  Troy University-Global Campus                                                                 |                |                    |                     |
|  Alaska Bible College                                                                          |                |                    |                     |
|  Global MBA Latin American Managers Program Satellite Campus                                   |                |                    |                     |
|  Frank Lloyd Wright School of Architecture                                                     |                |                    |                     |
|  Xavier University of Louisiana                                                                | 43200          | 13300              | 127300              |
|  Cabrillo College                                                                              | 43300          | 6100               | 81800               |
|  University of San Diego                                                                       | 43400          | 14500              | 113700              |
|  De Anza College                                                                               | 43500          | 8400               | 98700               |
|  Alfred University                                                                             | 43500          | 13400              | 84700               |
|  Santa Barbara City College                                                                    | 43600          | 5200               | 80600               |
|  Loyola Marymount University                                                                   | 43800          | 17300              | 113000              |
|  Art Center College of Design                                                                  | 43900          | 7600               | 114700              |
|  Hesston College                                                                               | 43900          | 9100               | 67500               |
|  University of Phoenix-Phoenix Campus                                                          | 44000          | 13300              | 110100              |
|  Saint Johns River State College                                                               | 44000          | 7100               | 64300               |
|  Dominican University of California                                                            | 44100          | 9700               | 124200              |
|  Menlo College                                                                                 | 44200          | 11000              | 115800              |
|  John Brown University                                                                         | 44300          | 11800              | 106800              |
|  University of Arkansas                                                                        | 44400          | 13000              | 87200               |
|  Wayne State University                                                                        | 44400          | 10100              | 93500               |
|  University of Hawaii at Manoa                                                                 | 44500          | 12200              | 89000               |
|  Michigan State University                                                                     | 44500          | 17200              | 98200               |
|  DePaul University                                                                             | 44700          | 12200              | 99700               |
|  Illinois Institute of Technology                                                              | 44800          | 22400              | 118200              |
|  Loyola University Maryland                                                                    | 44800          | 24400              | 123600              |
|  Bates College                                                                                 | 44900          | 17500              | 114000              |
|  American University                                                                           | 45000          | 15000              | 110700              |
|  Highlands College of Montana Tech                                                             | 45000          | 10300              | 103700              |
|  Montana Tech of the University of Montana                                                     | 45000          | 10300              | 103700              |
|  The New England Conservatory of Music                                                         | 45200          | 5500               | 68400               |
|  Thomas Edison State College                                                                   | 45200          | 7000               | 115000              |
|  University of Missouri-Kansas City                                                            | 45300          | 11200              | 109500              |
|  Pomona College                                                                                | 45500          | 17200              | 133700              |
|  Notre Dame de Namur University                                                                | 45600          | 12100              | 96200               |
|  Thomas More College                                                                           | 45800          | 12500              | 97100               |
|  Auburn University                                                                             | 45900          | 13800              | 91400               |
|  Fairfield University                                                                          | 45900          | 28300              | 125500              |
|  Quinnipiac University                                                                         | 45900          | 21100              | 102400              |
|  University of Denver                                                                          | 46100          | 13000              | 105000              |
|  Palmer College of Chiropractic-Davenport                                                      | 46100          | 8600               | 100200              |
|  California Maritime Academy                                                                   | 46200          | 18800              | 141200              |
|  University of Colorado Boulder                                                                | 46200          | 12700              | 99400               |
|  Colorado School of Mines                                                                      | 46200          | 25400              | 136700              |
|  Mills College                                                                                 | 46400          | 6400               | 81300               |
|  Boston University                                                                             | 46400          | 19500              | 119600              |
|  Loyola University Chicago                                                                     | 46600          | 15900              | 96900               |
|  Drake University                                                                              | 46600          | 20100              | 130200              |
|  Samford University                                                                            | 46700          | 12600              | 124000              |
|  Louisiana State University Health Sciences Center-New Orleans                                 | 46800          | 25400              | 117200              |
|  California Western School of Law                                                              | 47100          | 23100              | 154300              |
|  MCPHS University                                                                              | 47100          | 36200              | 155500              |
|  Academy of Art University                                                                     | 47300          | 5900               | 90600               |
|  University of San Francisco                                                                   | 47300          | 18000              | 122100              |
|  Illinois College of Optometry                                                                 | 47400          | 27000              | 142500              |
|  University of California-San Diego                                                            | 47800          | 17800              | 122700              |
|  Albany College of Pharmacy and Health Sciences                                                | 47900          | 33000              | 151900              |
|  Foothill College                                                                              | 48000          | 7300               | 117600              |
|  Maine Maritime Academy                                                                        | 48000          | 22900              | 151100              |
|  Carleton College                                                                              | 48100          | 11800              | 105200              |
|  University of Louisville                                                                      | 48500          | 10200              | 76600               |
|  Loma Linda University                                                                         | 48900          | 22600              | 133800              |
|  University of California-Davis                                                                | 49100          | 16900              | 117500              |
|  St Louis College of Pharmacy                                                                  | 49100          | 31800              | 147900              |
|  Bentley University                                                                            | 49200          | 30100              | 130700              |
|  The University of Alabama                                                                     | 49300          | 13100              | 85000               |
|  Louisiana State University and Agricultural & Mechanical College                              | 49400          | 14400              | 96600               |
|  Mount St Mary's College                                                                       | 49500          | 14300              | 103700              |
|  Mount St. Mary's College - Doheny Campus                                                      | 49500          | 14300              | 103700              |
|  Connecticut Center for Massage Therapy-Newington                                              | 49700          | 5000               | 71600               |
|  Saint Mary's College of California                                                            | 49800          | 15500              | 127400              |
|  College of the Canyons                                                                        | 50300          | 5400               | 79400               |
|  Harvey Mudd College                                                                           | 50800          | 24500              | 146900              |
|  Saint Johns University                                                                        | 50900          | 26100              | 107400              |
|  William Mitchell College of Law                                                               | 51000          | 31500              | 148300              |
|  Georgia Institute of Technology-Main Campus                                                   | 51100          | 23700              | 130000              |
|  Life University                                                                               | 51100          | 7100               | 90300               |
|  Los Medanos College                                                                           | 51600          | 4000               | 79900               |
|  Charles R Drew University of Medicine and Science                                             | 52200          | 7900               | 136200              |
|  University of Maryland-College Park                                                           | 52200          | 19100              | 111500              |
|  University of Iowa                                                                            | 52300          | 17300              | 101700              |
|  University of Illinois at Urbana-Champaign                                                    | 53000          | 20800              | 112000              |
|  University of Illinois at Chicago                                                             | 53200          | 14300              | 106700              |
|  University of Mississippi                                                                     | 53600          | 13200              | 96700               |
|  University of Mississippi Medical Center                                                      | 53600          | 13200              | 96700               |
|  Maine College of Art                                                                          | 53700          | 4300               | 45100               |
|  College of the Holy Cross                                                                     | 53900          | 31000              | 136800              |
|  Brandeis University                                                                           | 54200          | 17900              | 121300              |
|  Berk Trade and Business School                                                                | 54200          | 3800               | 83600               |
|  Southwestern Law School                                                                       | 54400          | 13600              | 147700              |
|  University of the Pacific                                                                     | 54500          | 15900              | 154800              |
|  Worcester Polytechnic Institute                                                               | 54700          | 28200              | 117100              |
|  California College of the Arts                                                                | 55000          | 3300               | 100300              |
|  Barnard College                                                                               | 55000          | 17400              | 127400              |
|  University of California-Los Angeles                                                          | 55200          | 13900              | 128000              |
|  Portfolio Center                                                                              | 55400          | 2900               | 137700              |
|  Marshall B Ketchum University                                                                 | 55600          | 17700              | 153900              |
|  Pepperdine University                                                                         | 56000          | 15200              | 137800              |
|  Stevens Institute of Technology                                                               | 56200          | 32100              | 135300              |
|  Claremont McKenna College                                                                     | 56500          | 18200              | 164000              |
|  Trinity College                                                                               | 56600          | 18200              | 126800              |
|  Golden Gate University-San Francisco                                                          | 57100          | 18200              | 122800              |
|  Golden Gate University-Los Angeles                                                            | 57100          | 18200              | 122800              |
|  Golden Gate University-Seattle                                                                | 57100          | 18200              | 122800              |
|  Golden Gate University-Silicon Valley                                                         | 57100          | 18200              | 122800              |
|  University of Southern California                                                             | 57100          | 15800              | 143900              |
|  National University of Health Sciences                                                        | 57100          | 6800               | 95900               |
|  George Washington University                                                                  | 57400          | 19300              | 137200              |
|  Bowdoin College                                                                               | 57800          | 15300              | 135100              |
|  Santa Clara University                                                                        | 57900          | 21600              | 139000              |
|  Colby College                                                                                 | 60500          | 15400              | 111700              |
|  Samuel Merritt University                                                                     | 62000          | 30700              | 194400              |
|  Rush University                                                                               | 62300          | 33600              | 242500              |
|  University of Maryland-Baltimore                                                              | 62300          | 35900              | 158600              |
|  Washington University in St Louis                                                             | 62300          | 20200              | 154300              |
|  Wesleyan University                                                                           | 62400          | 11400              | 105200              |
|  Wellesley College                                                                             | 62800          | 18600              | 121300              |
|  University of Michigan-Ann Arbor                                                              | 62900          | 17200              | 128000              |
|  University of California-Berkeley                                                             | 64300          | 16200              | 149700              |
|  University of Colorado Denver                                                                 | 64400          | 21700              | 157000              |
|  Coffeyville Community College                                                                 | 64700          | 5100               | 64800               |
|  Coffeyville Technical Campus                                                                  | 64700          | 5100               | 64800               |
|  Columbus Technical Campus                                                                     | 64700          | 5100               | 64800               |
|  Johns Hopkins University                                                                      | 65000          | 23400              | 148600              |
|  Emory University                                                                              | 65800          | 18300              | 135900              |
|  Tulane University of Louisiana                                                                | 65900          | 13700              | 126000              |
|  University of Miami                                                                           | 67800          | 12300              | 112900              |
|  Albany Law School                                                                             | 70300          | 16700              | 134600              |
|  Boston College                                                                                | 70400          | 24200              | 160300              |
|  University of Nebraska Medical Center                                                         | 71600          | 29300              | 159300              |
|  California Institute of the Arts                                                              | 72400          | 5400               | 96900               |
|  Williams College                                                                              | 75100          | 16800              | 167700              |
|  University of Notre Dame                                                                      | 75200          | 26000              | 154400              |
|  Midwestern University-Downers Grove                                                           | 78000          | 43500              | 244200              |
|  Northwestern University                                                                       | 80500          | 16800              | 173600              |
|  Tufts University                                                                              | 86100          | 21600              | 170300              |
|  Babson College                                                                                | 87000          | 36700              | 186700              |
|  University of California-San Francisco                                                        | 87900          | 40300              | 250000              |
|  Georgetown University                                                                         | 92300          | 28500              | 221900              |
|  Western University of Health Sciences                                                         | 94100          | 33200              | 248500              |
|  Dartmouth College                                                                             | 94100          | 16900              | 210500              |
|  University of Chicago                                                                         | 98700          | 16700              | 195000              |
|  University of California-Hastings College of Law                                              | 100700         | 25800              | 240200              |
|  Yale University                                                                               | 100800         | 15400              | 184800              |
|  Monterey Institute of International Studies                                                   | 106400         | 13900              | 165400              |
|  Rosalind Franklin University of Medicine and Science                                          | 106400         | 53000              | 250000              |
|  California Institute of Technology                                                            | 111800         | 19900              | 189000              |
|  Princeton University                                                                          | 115600         | 20800              | 217200              |
|  Amherst College                                                                               | 123900         | 18200              | 172500              |
|  Harvard University                                                                            | 127000         | 24700              | 250000              |
|  Massachusetts Institute of Technology                                                         | 143900         | 30400              | 242300              |
|------------------------------------------------------------------------------------------------+----------------+--------------------+---------------------|
```

(note: 250000 as such a round number? That must be a cutoff point for "Over 250000". No way both Rosalind Franklin and Harvard both stop at exactly the same point and it's equal to "one quarter million, exactly"?)




Theoretical SD's are easy, once you've learnt the topic. But data SD's are much harder for me to think about (since the distribution isn't normal and wasn't pre-transformed to look normal before calculating SD). It's certainly a measure of spread, but the quantiles (and in nice level of detail!) are









# My income inequality measure is bad

```{r}
earnings %>% filter(income_inequality > 3) %>% select(INSTNM)
```



## 90/10 ratio, 10 years on

all across the US, by school..


```{r}
earnings$pct90_earn_wne_p10 / earnings$pct10_earn_wne_p10 -> earnings$ninety_ten_ratio_p10
earnings$ninety_ten_ratio_p10 %>% stem
#thanks sitting bull
earnings %>% filter(ninety_ten_ratio_p10 > 30) %>% select(INSTNM, md_earn_wne_p10, mn_earn_wne_p10, faminc, pct_black)
#what are income levels like for these crazy 90/10 ratios?
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(INSTNM, md_earn_wne_p10, mn_earn_wne_p10, faminc, pct_black, pct_white, pct_born_us) %>% summary
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(md_earn_wne_p10, mn_earn_wne_p10, faminc) %>% sapply(stem)
par(mfrow=c(3,1))
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(md_earn_wne_p10, mn_earn_wne_p10, faminc) %>% sapply(kd)   #my kernel-density plot. prettified plot( density( x )): basically a histogram.
par(mfrow=c(3,1))
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(md_earn_wne_p10) %>% unlist %>% kd
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(mn_earn_wne_p10) %>% unlist %>% kd
earnings %>% filter(ninety_ten_ratio_p10 > 20) %>% select(faminc) %>% unlist %>% na.omit %>% kd
```



# Useful filters to keep in mind

- `filter(income_inequality < 3)`



I guess what is an "outlier" and what is "relevant" is a matter of what you're asking about. I'm just like newspapers / online magazines: I'm interested in the Ivy league masters of the universe and how rich I could be now if I'd only gotten into X.
















# Vow of Poverty

10th percentile, 10 years on, of those who went to the fancy schools:


`<earnings csvcut -c 2,43,49,52 | grep -v Privacy | csvsort -c 2 | csvcut -c1,3 | csvlook`


```
<earnings csvcut -c 2,43,49,52 | grep -v Privacy | csvsort -c 2 | csvcut -c1,3 | sed 's/,/: $/'
Bentley University: $30100
The University of Alabama: $13100
Louisiana State University and Agricultural & Mechanical College: $14400
Mount St Mary's College: $14300
Mount St. Mary's College - Doheny Campus: $14300
Connecticut Center for Massage Therapy-Newington: $5000
Saint Mary's College of California: $15500
College of the Canyons: $5400
Harvey Mudd College: $24500
Saint Johns University: $26100
William Mitchell College of Law: $31500
Georgia Institute of Technology-Main Campus: $23700
Life University: $7100
Los Medanos College: $4000
Charles R Drew University of Medicine and Science: $7900
University of Maryland-College Park: $19100
University of Iowa: $17300
University of Illinois at Urbana-Champaign: $20800
University of Illinois at Chicago: $14300
University of Mississippi: $13200
University of Mississippi Medical Center: $13200
Maine College of Art: $4300
College of the Holy Cross: $31000
Brandeis University: $17900
Berk Trade and Business School: $3800
Southwestern Law School: $13600
University of the Pacific: $15900
Worcester Polytechnic Institute: $28200
California College of the Arts: $3300
Barnard College: $17400
University of California-Los Angeles: $13900
Portfolio Center: $2900
Marshall B Ketchum University: $17700
Pepperdine University: $15200
Stevens Institute of Technology: $32100
Claremont McKenna College: $18200
Trinity College: $18200
Golden Gate University-San Francisco: $18200
Golden Gate University-Los Angeles: $18200
Golden Gate University-Seattle: $18200
Golden Gate University-Silicon Valley: $18200
University of Southern California: $15800
National University of Health Sciences: $6800
George Washington University: $19300
Bowdoin College: $15300
Santa Clara University: $21600
Colby College: $15400
Samuel Merritt University: $30700
Rush University: $33600
University of Maryland-Baltimore: $35900
Washington University in St Louis: $20200
Wesleyan University: $11400
Wellesley College: $18600
University of Michigan-Ann Arbor: $17200
University of California-Berkeley: $16200
University of Colorado Denver: $21700
Coffeyville Community College: $5100
Coffeyville Technical Campus: $5100
Columbus Technical Campus: $5100
Johns Hopkins University: $23400
Emory University: $18300
Tulane University of Louisiana: $13700
University of Miami: $12300
Albany Law School: $16700
Boston College: $24200
University of Nebraska Medical Center: $29300
California Institute of the Arts: $5400
Williams College: $16800
University of Notre Dame: $26000
Midwestern University-Downers Grove: $43500
Northwestern University: $16800
Tufts University: $21600
Babson College: $36700
University of California-San Francisco: $40300
Georgetown University: $28500
Western University of Health Sciences: $33200
Dartmouth College: $16900
University of Chicago: $16700
University of California-Hastings College of Law: $25800
Yale University: $15400
Monterey Institute of International Studies: $13900
Rosalind Franklin University of Medicine and Science: $53000
California Institute of Technology: $19900
Princeton University: $20800
Amherst College: $18200
Harvard University: $24700
Massachusetts Institute of Technology: $30400
```


```
<earnings csvcut -c 2,43,49,52,48 | grep -v Privacy | csvsort -c 2 | csvcut -c1,3,5 | (head -1; tail -25) | csvlook
<earnings csvcut -c 2,43,49,52,48 | grep -v Privacy | csvsort -c 2 | csvcut -c1,3,5 | (head -1; tail -55) | sed 's/,/: $/' | sed 's/,/ (average: $/' | sed 's/$/\)/'
INSTNM: $pct10_earn_wne_p10 (average: $md_earn_wne_p10)
University of Nevada-Reno: $12700 (average: $45500)
Bethune-Cookman University: $6800 (average: $28700)
Butler University: $19500 (average: $52400)
Southern Arkansas University Main Campus: $9800 (average: $35900)
Le Cordon Bleu College of Culinary Arts-San Francisco: $7100 (average: $32800)
Sacred Heart University: $17100 (average: $54100)
Northwestern Health Sciences University: $8200 (average: $42500)
California State University-Fresno: $10000 (average: $43200)
Jacksonville University: $13800 (average: $47700)
Le Cordon Bleu College of Culinary Arts-Chicago: $7500 (average: $32800)
Michigan Technological University: $18100 (average: $60100)
University of Minnesota-Twin Cities: $16100 (average: $47800)
University of Nebraska-Lincoln: $16100 (average: $43800)
Nebraska College of Technical Agriculture: $16100 (average: $43800)
University of the Southwest: $10400 (average: $40600)
Wheaton College: $7700 (average: $42600)
Ringling College of Art and Design: $6900 (average: $32800)
University of Florida: $15900 (average: $51300)
Mercer University: $13400 (average: $46600)
University of Arizona: $12100 (average: $44400)
University of Minnesota-Duluth: $15300 (average: $43300)
Drew University: $13100 (average: $50900)
University of Arkansas for Medical Sciences: $24500 (average: $62400)
Kalamazoo College: $10600 (average: $49400)
University of South Alabama: $10500 (average: $38300)
Alaska Pacific University: $10800 (average: $47400)
University of California-Santa Barbara: $13500 (average: $52000)
Mississippi College: $11700 (average: $38200)
Holy Names University: $10600 (average: $50100)
Logan University: $6700 (average: $36200)
University of Georgia: $14200 (average: $46500)
Lake Forest College: $14300 (average: $48100)
University of Missouri-Columbia: $16200 (average: $46000)
Divers Academy International: $10100 (average: $48700)
DePauw University: $16700 (average: $47800)
Massachusetts Maritime Academy: $26300 (average: $79500)
Colorado Technical University-Colorado Springs: $11800 (average: $44100)
Louisiana Tech University: $11700 (average: $41100)
Olivet Nazarene University: $9600 (average: $37700)
Bellevue University: $18200 (average: $52200)
Creighton University: $22800 (average: $57800)
Rensselaer Hartford Graduate Center Inc: $37000 (average: $81700)
Trinity Christian College: $11300 (average: $41400)
Northeastern University: $18800 (average: $60100)
Rutgers University-Camden: $15400 (average: $54800)
Rutgers University-New Brunswick: $15400 (average: $54800)
Rutgers University-Newark: $15400 (average: $54800)
Regis University: $15100 (average: $53100)
California Polytechnic State University-San Luis Obispo: $15700 (average: $60900)
University of Connecticut: $19000 (average: $53900)
National Louis University: $9600 (average: $43700)
Beth Medrash Govoha: $3500 (average: $23000)
William Penn University: $10700 (average: $41200)
San Jose State University: $13200 (average: $54600)
Xavier University of Louisiana: $13300 (average: $46500)
Cabrillo College: $6100 (average: $32100)
University of San Diego: $14500 (average: $56300)
De Anza College: $8400 (average: $43600)
Alfred University: $13400 (average: $42300)
Santa Barbara City College: $5200 (average: $33900)
Loyola Marymount University: $17300 (average: $55600)
Art Center College of Design: $7600 (average: $51700)
Hesston College: $9100 (average: $35400)
University of Phoenix-Phoenix Campus: $13300 (average: $53400)
Saint Johns River State College: $7100 (average: $29500)
Dominican University of California: $9700 (average: $51400)
Menlo College: $11000 (average: $50600)
John Brown University: $11800 (average: $46200)
University of Arkansas: $13000 (average: $43600)
Wayne State University: $10100 (average: $41500)
University of Hawaii at Manoa: $12200 (average: $44300)
Michigan State University: $17200 (average: $49800)
DePaul University: $12200 (average: $50900)
Illinois Institute of Technology: $22400 (average: $68200)
Loyola University Maryland: $24400 (average: $62100)
Bates College: $17500 (average: $53500)
American University: $15000 (average: $55900)
Highlands College of Montana Tech: $10300 (average: $39800)
Montana Tech of the University of Montana: $10300 (average: $39800)
The New England Conservatory of Music: $5500 (average: $29500)
Thomas Edison State College: $7000 (average: $49100)
University of Missouri-Kansas City: $11200 (average: $43100)
Pomona College: $17200 (average: $52600)
Notre Dame de Namur University: $12100 (average: $51300)
Thomas More College: $12500 (average: $45800)
Auburn University: $13800 (average: $45400)
Fairfield University: $28300 (average: $69000)
Quinnipiac University: $21100 (average: $56400)
University of Denver: $13000 (average: $51400)
Palmer College of Chiropractic-Davenport: $8600 (average: $39700)
California Maritime Academy: $18800 (average: $81100)
University of Colorado Boulder: $12700 (average: $48000)
Colorado School of Mines: $25400 (average: $74700)
Mills College: $6400 (average: $39000)
Boston University: $19500 (average: $60600)
Loyola University Chicago: $15900 (average: $50600)
Drake University: $20100 (average: $55700)
Samford University: $12600 (average: $45800)
Louisiana State University Health Sciences Center-New Orleans: $25400 (average: $61100)
California Western School of Law: $23100 (average: $85900)
MCPHS University: $36200 (average: $116400)
Academy of Art University: $5900 (average: $36100)
University of San Francisco: $18000 (average: $61000)
Illinois College of Optometry: $27000 (average: $81400)
University of California-San Diego: $17800 (average: $59600)
Albany College of Pharmacy and Health Sciences: $33000 (average: $110600)
Foothill College: $7300 (average: $47600)
Maine Maritime Academy: $22900 (average: $74700)
Carleton College: $11800 (average: $46100)
University of Louisville: $10200 (average: $37700)
Loma Linda University: $22600 (average: $72800)
University of California-Davis: $16900 (average: $57100)
St Louis College of Pharmacy: $31800 (average: $111600)
Bentley University: $30100 (average: $74900)
The University of Alabama: $13100 (average: $42400)
Louisiana State University and Agricultural & Mechanical College: $14400 (average: $45900)
Mount St Mary's College: $14300 (average: $50200)
Mount St. Mary's College - Doheny Campus: $14300 (average: $50200)
Connecticut Center for Massage Therapy-Newington: $5000 (average: $27300)
Saint Mary's College of California: $15500 (average: $59000)
College of the Canyons: $5400 (average: $34200)
Harvey Mudd College: $24500 (average: $78600)
Saint Johns University: $26100 (average: $55900)
William Mitchell College of Law: $31500 (average: $68200)
Georgia Institute of Technology-Main Campus: $23700 (average: $74000)
Life University: $7100 (average: $32200)
Los Medanos College: $4000 (average: $34300)
Charles R Drew University of Medicine and Science: $7900 (average: $63000)
University of Maryland-College Park: $19100 (average: $59100)
University of Iowa: $17300 (average: $48700)
University of Illinois at Urbana-Champaign: $20800 (average: $56600)
University of Illinois at Chicago: $14300 (average: $51600)
University of Mississippi: $13200 (average: $40600)
University of Mississippi Medical Center: $13200 (average: $40600)
Maine College of Art: $4300 (average: $23700)
College of the Holy Cross: $31000 (average: $63700)
Brandeis University: $17900 (average: $58800)
Berk Trade and Business School: $3800 (average: $33700)
Southwestern Law School: $13600 (average: $69700)
University of the Pacific: $15900 (average: $66400)
Worcester Polytechnic Institute: $28200 (average: $77600)
California College of the Arts: $3300 (average: $35700)
Barnard College: $17400 (average: $57400)
University of California-Los Angeles: $13900 (average: $59200)
Portfolio Center: $2900 (average: $47900)
Marshall B Ketchum University: $17700 (average: $70400)
Pepperdine University: $15200 (average: $61400)
Stevens Institute of Technology: $32100 (average: $82800)
Claremont McKenna College: $18200 (average: $63600)
Trinity College: $18200 (average: $56100)
Golden Gate University-San Francisco: $18200 (average: $64200)
Golden Gate University-Los Angeles: $18200 (average: $64200)
Golden Gate University-Seattle: $18200 (average: $64200)
Golden Gate University-Silicon Valley: $18200 (average: $64200)
University of Southern California: $15800 (average: $66100)
National University of Health Sciences: $6800 (average: $45400)
George Washington University: $19300 (average: $64500)
Bowdoin College: $15300 (average: $54800)
Santa Clara University: $21600 (average: $67700)
Colby College: $15400 (average: $53000)
Samuel Merritt University: $30700 (average: $111500)
Rush University: $33600 (average: $74300)
University of Maryland-Baltimore: $35900 (average: $80400)
Washington University in St Louis: $20200 (average: $62300)
Wesleyan University: $11400 (average: $50900)
Wellesley College: $18600 (average: $56700)
University of Michigan-Ann Arbor: $17200 (average: $57900)
University of California-Berkeley: $16200 (average: $62700)
University of Colorado Denver: $21700 (average: $73800)
Coffeyville Community College: $5100 (average: $29800)
Coffeyville Technical Campus: $5100 (average: $29800)
Columbus Technical Campus: $5100 (average: $29800)
Johns Hopkins University: $23400 (average: $69200)
Emory University: $18300 (average: $59000)
Tulane University of Louisiana: $13700 (average: $52400)
University of Miami: $12300 (average: $52400)
Albany Law School: $16700 (average: $71200)
Boston College: $24200 (average: $67000)
University of Nebraska Medical Center: $29300 (average: $64200)
California Institute of the Arts: $5400 (average: $32500)
Williams College: $16800 (average: $58100)
University of Notre Dame: $26000 (average: $69400)
Midwestern University-Downers Grove: $43500 (average: $117000)
Northwestern University: $16800 (average: $64100)
Tufts University: $21600 (average: $67800)
Babson College: $36700 (average: $85500)
University of California-San Francisco: $40300 (average: $118900)
Georgetown University: $28500 (average: $83300)
Western University of Health Sciences: $33200 (average: $123200)
Dartmouth College: $16900 (average: $67100)
University of Chicago: $16700 (average: $62800)
University of California-Hastings College of Law: $25800 (average: $107900)
Yale University: $15400 (average: $66000)
Monterey Institute of International Studies: $13900 (average: $53400)
Rosalind Franklin University of Medicine and Science: $53000 (average: $166200)
California Institute of Technology: $19900 (average: $74000)
Princeton University: $20800 (average: $75100)
Amherst College: $18200 (average: $56800)
Harvard University: $24700 (average: $87200)
Massachusetts Institute of Technology: $30400 (average: $91600)
```






# more observations
- caltech family income is way lower than MIT family income






# rich kid schools

```{r}
earnings %>% filter(faminc > 100000) %>% select(INSTNM,dependent,veteran,married,pct_black,mn_earn_wne_p6,pct10_earn_wne_p10,pct25_earn_wne_p10,pct75_earn_wne_p10,pct90_earn_wne_p10, gt_25k_p10)
```

Look at chance of being poor (<25k) or rich (90th percentile) for 


Maybe average quantiles across these school types?


Also want to do a straight-up regression on this.
```{r does.rich.family.make.you.rich}
#top 90 percent per your school?
lm( data=earnings, pct90_earn_wne_p10 ~ faminc )
lm( data=earnings, pct90_earn_wne_p10 ~ lnfaminc )   #what does this mean?! try with square term
#prevent poverty?
lm( data=earnings, gt_25k_p6 ~ faminc )
lm( data=earnings, gt_25k_p10 ~ faminc ) #hmm, at least the beta (amount of influence) goes down from 6-10 years .. a bit
#typical income
lm( data=earnings, mn_earn_wne_p6 ~ faminc )
lm( data=earnings, mn_earn_wne_p10 ~ faminc )
#now that's weird ... family income has more impact on *10-year* mean earnings than on 6-year … even though the likelihood of getting out of >25k becomes less influential...
#holds up in rlm's as well...
rlm( data=earnings, mn_earn_wne_p6 ~ faminc )
rlm( data=earnings, mn_earn_wne_p10 ~ faminc )
#… throw in square term as well 
```

(and of course run these too with `MASS::rlm`)


(obviously this is not on an individual level. but still a differetn way to crosscut some tax data that people might not have studied otherwise [^how would you get family's income except through a FAFSA?]






# cosmetology, nontraditional medicine, and success schools

I would like to figure out how to disseminate the government-provided information in a way that's more appropriate than GitHub, to reach the target market for cosmetology schools, beauty schools, school of success, etc. Just from browsing this data-set, the low incomes and terrible performance of these schools keeps showing up in my statistics. On the other hand, there's a low chance that the target students are curling the government's open-data API.

Maybe pamphlets? I could make a LaTeX or Rmd pamphlet, generate printable PDF's about each of the really poorly performing schools, and then leave it up to people in the target geography to disseminate the pamphlets?

Maybe websites? I could make an HTML page with the equivalent information about the pamphlet, upload the static site to S3, and then target the name of the poorly performing schools in google ads? (Or do these people use another search engine?!?)

I don't really want to pay for printing, distribution, or google ads though.
